The CrypTool Script: \\ Cryptography, Mathematics and More \\ \vspace{30pt} {\large Background reading\\%*[-8pt] for the free eLearning program CrypTool\\ (10th edition -- distributed with CrypTool version 1.4.30)} \vspace{60pt}

### 2009-07-08 script/de/chapters/numbertheory.tex
CT script: links updated in German and English

\vskip +10pt
Die letzten Rekorde\footnote{%
Die  "`RSA-Zahlen"' sind große semiprime Zahlen (d.h. Zahlen, die genau aus
2 Primfaktoren bestehen)\index{Zahlen!semiprime}. Sie wurden von der Firma
RSA Security generiert und veröffentlicht, und sie bilden die "`RSA Factoring
Challenge"': In diesem Wettbewerb werden die Primfaktoren dieser Zahlen
gesucht.
Siehe \href{http://www.rsasecurity.com/rsalabs/challenges/factoring/numbers.html}
   {\texttt{http://www.rsasecurity.com/rsalabs/challenges/factoring/numbers.html}}.

@@

\begin{table}[h]
\begin{center}
\begin{tabular}{|c|ccccc|}
\hline
   & {\bf Dezimalstellen} & {\bf Binärstellen} & & {\bf Faktorisiert am} & {\bf Faktorisiert von} \\
\hline
	RSA-155	&	155 & 512 & & August, 1999 & Herman te Riele et al. \\
	C158 & 		158 & 523 & & Januar, 2002 & Jens Franke et al. \\
	RSA-160 & 	160 & 530 & & April, 2003 & Jens Franke et al. \\
	RSA576 & 	174 & 576 & & Dezember, 2003 & Jens Franke et al. \\
	C176 & 		176 & 583 & & Mai, 2005 & Kazumaro Aoki et al. \\
	RSA640\footnotemark & 	193 & 600 & & November, 2005 & Jens Franke et al. \\
	RSA-200 & 	200 & 663 & & Mai, 2005 & Jens Franke et al. \\
	C307 & 		307 & 1017 & & Mai, 2007 & Jens Franke et al. \\
\hline
\end{tabular}
\caption{Die derzeitigen Faktorisierungsrekorde (Stand Juni 2007)}    % Eyecatcher_neue-Mersenne
\end{center}
\end{table}
\footnotetext{%
Eine Arbeitsgruppe des BSI hat die mit 20.000 US-Dollar dotierte Challenge
RSA-640 mit Hilfe der GNFS-Methode gelöst. Die Forscher benötigten für die
Zerlegung der Zahl in ihre beiden 320 Bit langen Primfaktoren rund fünf
Monate Rechenzeit.\\
Die RSA-Laboratorien schreiben ihre Challenges schon seit Anfang der
90er-Jahre aus. Die nächst größere Challenge ist nun die mit 30.000
US-Dollar dotierte RSA-704.\\
Siehe:
\href{http://www.heise.de/newsticker/meldung/print/65957}
{\texttt{http://www.heise.de/newsticker/meldung/print/65957}}
}
%be_2005: Erzwingen, dass die Abb. noch in diesem Kapitel !

@@

\bibitem[Shamir2003a]{Shamir2003a} \index{Shamir 2003a} \index{TWIRL-Device} 
    Adi Shamir, Eran Tromer, \\
    {\em On the Cost of Factoring RSA-1024}, 
    RSA Laboratories CryptoBytes Volume 6, No. 2, Summer 2003, S. 11-20 \\
    \href{http://www.rsasecurity.com/rsalabs/cryptobytes/CryptoBytes\_August\_2003.pdf}
    {\texttt{http://www.rsasecurity.com/rsalabs/cryptobytes/CryptoBytes\_August\_2003.pdf}}

@@

         \href{http://www.rsasecurity.com/rsalabs/challenges/factoring/numbers.html}
           {\texttt{http://www.rsasecurity.com/rsalabs/challenges/factoring/numbers.html}}

>>>>

\vskip +10pt
Die letzten Rekorde\footnote{%
Die  "`RSA-Zahlen"' sind große semiprime Zahlen (d.h. Zahlen, die genau aus
2 Primfaktoren bestehen)\index{Zahlen!semiprime}. Sie wurden von der Firma
RSA Security generiert und veröffentlicht, und sie bilden die "`RSA Factoring
Challenge"': In diesem Wettbewerb werden die Primfaktoren dieser Zahlen
gesucht.
Siehe \href{http://www.rsa.com/rsalabs/node.asp?id=2092}
   {\texttt{http://www.rsa.com/rsalabs/node.asp?id=2092}}.

@@

\begin{table}[h]
\begin{center}
\begin{tabular}{|c|ccccc|}
\hline
   & {\bf Dezimalstellen} & {\bf Binärstellen} & & {\bf Faktorisiert am} & {\bf Faktorisiert von} \\
\hline
	RSA-155	&	155 & 512 & & August, 1999 & Herman te Riele et al. \\
	C158 & 		158 & 523 & & Januar, 2002 & Jens Franke et al. \\
	RSA-160 & 	160 & 530 & & April, 2003 & Jens Franke et al. \\
	RSA576 & 	174 & 576 & & Dezember, 2003 & Jens Franke et al. \\
	C176 & 		176 & 583 & & Mai, 2005 & Kazumaro Aoki et al. \\
	RSA640\footnotemark & 	193 & 600 & & November, 2005 & Jens Franke et al. \\
	RSA-200 & 	200 & 663 & & Mai, 2005 & Jens Franke et al. \\
	C307 & 		307 & 1017 & & Mai, 2007 & Jens Franke et al. \\
\hline
\end{tabular}
\caption{Die derzeitigen Faktorisierungsrekorde (Stand Juli 2009)}    % Eyecatcher_neue-Mersenne
\end{center}
\end{table}
\footnotetext{%
Eine Arbeitsgruppe des BSI hat die mit 20.000 US-Dollar dotierte Challenge
RSA-640 mit Hilfe der GNFS-Methode gelöst. Die Forscher benötigten für die
Zerlegung der Zahl in ihre beiden 320 Bit langen Primfaktoren rund fünf
Monate Rechenzeit.\\
Die RSA-Laboratorien schreiben ihre Challenges schon seit Anfang der
90er-Jahre aus. Die nächst größere Challenge ist nun die mit 30.000
US-Dollar dotierte RSA-704.\\
Siehe:
\href{http://www.heise.de/newsticker/meldung/print/65957}
{\texttt{http://www.heise.de/newsticker/meldung/print/65957}}
}
%be_2005: Erzwingen, dass die Abb. noch in diesem Kapitel !

@@

\bibitem[Shamir2003a]{Shamir2003a} \index{Shamir 2003a} \index{TWIRL-Device} 
    Adi Shamir, Eran Tromer, \\
    {\em On the Cost of Factoring RSA-1024}, 
    RSA Laboratories CryptoBytes Volume 6, No. 2, Summer 2003, S. 11-20 \\
    \href{http://www.rsasecurity.com/rsalabs/cryptobytes/CryptoBytes_August_2003.pdf}
    {\texttt{http://www.rsasecurity.com/rsalabs/cryptobytes/CryptoBytes\_August\_2003.pdf}}

@@

         \href{http://www.rsa.com/rsalabs/node.asp?id=2092}
           {\texttt{http://www.rsa.com/rsalabs/node.asp?id=2092}}

### 2009-07-08 script/en/chapters/numbertheory.tex
CT script: links updated in German and English

\vskip +10pt
The last records\footnote{%
The 'RSA numbers' are certain large semiprime numbers (i.e., numbers with
exactly two prime factors)\index{Number!semi prime}. 
They were generated and published by the 
company RSA Security and they form the basis of the RSA Factoring 
Challenge, in which factorisations for these numbers are sought.
See \href{http://www.rsasecurity.com/rsalabs/challenges/factoring/numbers.html}
 {\texttt{http://www.rsasecurity.com/rsalabs/challenges/factoring/numbers.html}}.

@@

\begin{table}[h]
\begin{center}
\begin{tabular}{|c|ccccc|}
\hline
	& {\bf Decimal digits} & {\bf Binary digits} & & {\bf Factored on} & {\bf Factored by} \\
\hline
	RSA-155	&	155 & 512 & & August, 1999 & Herman te Riele et al. \\
	C158 & 		158 & 523 & & January, 2002 & Jens Franke et al. \\
	RSA-160 & 	160 & 530 & & April, 2003 & Jens Franke et al. \\
	RSA576 & 	174 & 576 & & December, 2003 & Jens Franke et al. \\
	C176 & 		176 & 583 & & May, 2005 & Kazumaro Aoki et al. \\
	RSA640\footnotemark & 	193 & 600 & & November, 2005 & Jens Franke et al. \\
	RSA-200 & 	200 & 663 & & May, 2005 & Jens Franke et al. \\
	C307 & 		307 & 1017 & & May, 2007 & Jens Franke et al. \\
\hline
\end{tabular}
\caption{The current factoring records (as of June 2007)}    % Eyecatcher_neue-Mersenne 
\end{center}
\end{table} 
\footnotetext{%
A research group of the GISA solved this challenge which was awarded with
20,000 US dollar using the GNFS method. The researchers needed about five
months to divide this number into its both 320 bit long prime factors.\\
RSA Labs offers its challenges since the beginning of the 1990th.
The next bigger challenge awarded with 30,000 US dollars is RSA-704.\\
See:
\href{http://www.heise.de/newsticker/meldung/print/65957}
{\texttt{http://www.heise.de/newsticker/meldung/print/65957}}
}

@@

\bibitem[Shamir2003a]{Shamir2003a} \index{Shamir 2003a} \index{TWIRL device} 
    Adi Shamir, Eran Tromer, \\
    {\em On the Cost of Factoring RSA-1024}, 
    RSA Laboratories CryptoBytes Volume 6, No. 2, Summer 2003, p. 11-20 \\
    \href{http://www.rsasecurity.com/rsalabs/cryptobytes/CryptoBytes\_August\_2003.pdf}
    {\texttt{http://www.rsasecurity.com/rsalabs/cryptobytes/CryptoBytes\_August\_2003.pdf}}

>>>>

\vskip +10pt
The last records\footnote{%
The 'RSA numbers' are certain large semiprime numbers (i.e., numbers with
exactly two prime factors)\index{Number!semi prime}. 
They were generated and published by the 
company RSA Security and they form the basis of the RSA Factoring 
Challenge, in which factorisations for these numbers are sought.
See \href{http://www.rsa.com/rsalabs/node.asp?id=2092}
 {\texttt{http://www.rsa.com/rsalabs/node.asp?id=2092}}.

@@

\begin{table}[h]
\begin{center}
\begin{tabular}{|c|ccccc|}
\hline
	& {\bf Decimal digits} & {\bf Binary digits} & & {\bf Factored on} & {\bf Factored by} \\
\hline
	RSA-155	&	155 & 512 & & August, 1999 & Herman te Riele et al. \\
	C158 & 		158 & 523 & & January, 2002 & Jens Franke et al. \\
	RSA-160 & 	160 & 530 & & April, 2003 & Jens Franke et al. \\
	RSA576 & 	174 & 576 & & December, 2003 & Jens Franke et al. \\
	C176 & 		176 & 583 & & May, 2005 & Kazumaro Aoki et al. \\
	RSA640\footnotemark & 	193 & 600 & & November, 2005 & Jens Franke et al. \\
	RSA-200 & 	200 & 663 & & May, 2005 & Jens Franke et al. \\
	C307 & 		307 & 1017 & & May, 2007 & Jens Franke et al. \\
\hline
\end{tabular}
\caption{The current factoring records (as of July 2009)}    % Eyecatcher_neue-Mersenne 
\end{center}
\end{table} 
\footnotetext{%
A research group of the GISA solved this challenge which was awarded with
20,000 US dollar using the GNFS method. The researchers needed about five
months to divide this number into its both 320 bit long prime factors.\\
RSA Labs offers its challenges since the beginning of the 1990th.
The next bigger challenge awarded with 30,000 US dollars is RSA-704.\\
See:
\href{http://www.heise.de/newsticker/meldung/print/65957}
{\texttt{http://www.heise.de/newsticker/meldung/print/65957}}
}

@@

\bibitem[Shamir2003a]{Shamir2003a} \index{Shamir 2003a} \index{TWIRL device} 
    Adi Shamir, Eran Tromer, \\
    {\em On the Cost of Factoring RSA-1024}, 
    RSA Laboratories CryptoBytes Volume 6, No. 2, Summer 2003, p. 11-20 \\
    \href{http://www.rsasecurity.com/rsalabs/cryptobytes/CryptoBytes_August_2003.pdf}
    {\texttt{http://www.rsasecurity.com/rsalabs/cryptobytes/CryptoBytes\_August\_2003.pdf}}
